---
title: 'Research integrity advisors census: optional comments'
author: "Adrian Barnett"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  word_document:
    toc: false
    reference_docx: rmarkdown-styles-reference.docx
---

```{r setup, include=FALSE}
# using formatting in Word document (see above)
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE, error=FALSE, comment='', dpi=400)
options(width=1000) # Wide pages
options(scipen=999) # avoid scientific presentation
source('99_functions.R')
library(dplyr)

# get the data, from 3_read_qualtrics_api.R
load('rdata/3_AnalysisReady.RData')
```

This document shows all the optional comments.  

Text _in italics_ is the direct wording from the survey

# _Any comments about when your role started or ended? (optional)_

```{r, results='asis'}
text = comments(indata = data, question = 'q2_4')
cat(text)
```

# _Do you have any comments on your training or time spent as a Research Integrity Advisor? (optional)_

```{r, results='asis'}
text = comments(indata = data, question = 'q3_4')
cat(text)
```

# _Do you have any comments on the advice you have provided or situations you have encountered? (optional)_

```{r, results='asis'}
text = comments(indata = data, question = 'q4_4')
cat(text)
```

# _Lastly, do you have comments about your role as a Research Integrity Advisor or about this research? (optional)_

```{r, results='asis'}
text = comments(indata = data, question = 'q5_3')
cat(text)
```

# _Have you provided advice about - Other, please specify_

```{r, results='asis'}
text = comments(indata = data, question = 'q4_2_15_text')
cat(text)
```

# _Do you agree or disagree with the following statements concerning your role - Other, please specify_

```{r, results='asis'}
text = comments(indata = data, question = 'q5_1_9_text')
cat(text)
```
